Flatiron cleaning

### 2021-10-07 Rmd/rdi analysis.Rmd
Cleaning step 7 - decrease number too much

# `r emo::ji("question_mark")` Reminders/Questions of each capping and calculations:

@@

  # 6.Add a 30 day rule to switch linenumber----
  # group_by(patientid, linenumber_new) %>% 
  # arrange(episodedate) %>% 
  # mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
  # mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
  # ungroup() %>% 
  # group_by(patientid) %>% 
  # mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
  # mutate(linenumber_new = linenumber_new + jump_line) %>% 
  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new"), as.factor))

@@

### How many lines did patients received as Neoadjuvant
`r emo::ji("question_mark")`  
Here are all the number of line that patients received as Neoadjuvant containing platinum or taxanes.  
<span style="color:red">**Should we include patients who got more than 1 line as Neoadjuvant?**</span>

@@

Here the lines for the 34 patient.
```{r, rows.print = 40}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
         drugname, episodedate, surgerydate, chemotherapy_type) %>%
  arrange(patientid, episodedate) %>% 
  distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
  select(-linenumber)

@@

`r emo::ji("question_mark")`  
Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
<span style="color:red">**Should we include patients who got a single drug as lot/line?**</span> like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
<span style="color:red">**Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others?**</span> `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev**</span>

```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
therapy_line1 <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
  select(patientid, linename, linenumber, linenumber_new, drug_count, drugname, therapy, treatment_sequence) %>%

  mutate(remove_linename_other = case_when(
    linenumber == 1 &
      # treatment_sequence == "neo + surg + adj" &
      drug_count == 1 &
      str_detect(linename, "platin|taxel")       ~ "keep",
    linenumber == 1 &
      drug_count == 2 &
      (
      (str_detect(linename, "platin") &
      str_detect(linename, "taxel")) |
      (str_detect(linename, "platin") &
      str_detect(linename, "Bev")) |
        (str_detect(linename, "taxel") &
      str_detect(linename, "Bev"))
      )                                           ~ "keep",
    linenumber == 1 &
      drug_count == 3 &
      str_detect(linename, "platin") &
      str_detect(linename, "taxel") &
      str_detect(linename, "Bev")                 ~ "keep",

    TRUE                                          ~ NA_character_,
  )) %>% 
  group_by(patientid) %>% 
  fill(remove_linename_other, .direction = "down") %>% 
  ungroup() %>% 
  filter(remove_linename_other == "keep") %>% 
  select(-remove_linename_other)

therapy_line1 %>% 
  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
         ) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

therapy_line1 %>% 
  filter(linenumber_new == 2, treatment_sequence == "neo + surg + adj") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

@@

Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of line in Chemotherapy only
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Chemotherapy only") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```
<span style="color:red">**Do we keep in the chemotherapy only patients?**</span>  
<br>

@@

***
<br>

<font size="10">Thanks! `r  emo::ji("party_popper")`</font>

@@

```{r}
Frontline <- Treatment %>% 
  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
    group_by(patientid, chemotherapy_type) %>% 
  mutate(linenumber_adj = dense_rank(linenumber_new)) %>%

@@

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE)
```

@@

## 2.Plots Clinical
<div class = "row">
<div class = "col-md-6">
```{r}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

@@

```{r Table 3}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           had_neo, had_adj,
           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p(
    # test.args = all_tests("chisq.test") ~ list(workspace=2e9)
    ) %>% bold_p(t = .05)
# tbl2 <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

## 2.Plots Treatment
<div class = "row">
<div class = "col-md-6">
```{r}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

@@

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
# OS by extentofdebulking
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

```{r Table 4}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              type = list(relative_dose_intensity ~ 'continuous'),
              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              type = list(relative_dose_intensity ~ 'continuous'),
              label = list(relative_dose_intensity ~ "cisplatin/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl_stack(list(tbl4, tbl3, tbl5, tbl6), quiet = TRUE)

tbl1 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "taxel/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

>>>>

# `r emo::ji("question_mark")` Reminders of each capping and formula:

@@

  group_by(patientid, chemotherapy_type) %>% 
  mutate(linenumber_adj = dense_rank(linenumber_new)) %>% 
  ungroup() %>% 
  # 6.Add a 30 day rule to switch linenumber----
  # group_by(patientid, linenumber_new) %>% 
  # arrange(episodedate) %>% 
  # mutate(episode_interval = episodedate - lag(episodedate), episode_interval = ifelse(is.na(episode_interval), 0, episode_interval)) %>%  # FDB58481AFFBB 48 days
  # mutate(jump_line = ifelse(episode_interval > 31, 1, 0)) %>% # FA019D2071321 >31
  # ungroup() %>% 
  # group_by(patientid) %>% 
  # mutate(jump_line = cumsum(jump_line)) %>% # F002DD2953889 fixed even when increase multiple time 
  # mutate(linenumber_new = linenumber_new + jump_line) %>% 
  #F002DD2953889 need to do 37 and 42 F0040EA299CF0, 35 F005602DA4DF0 => do at least 37

  # 7.Calculate cycle for each line----
  mutate(cycle_drugname = str_remove(drugname, " protein-bound")) %>%  # F003F2BEEDB37 need to change drugname pacli = pacli bp
  group_by(patientid, linenumber_new, cycle_drugname) %>% # Wrong line name F001443D8B85C ~~~~~~~~~~~~~~~~~~~~~~~~~~ Fix later QUESTION Dr Chern is ok
  mutate(drugname_count_perline = n()) %>%  # F0000AD999ABF
  ungroup() %>% 
  mutate(across(c("linenumber", "linenumber_new", "linenumber_adj"), as.factor))

@@

```{r}
therapy_line %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(chemotherapy_type, therapy, treatment_sequence) %>% 
  tbl_summary(by = therapy)
```

### How many lines did patients received as Neoadjuvant
`r emo::ji("question_mark")`  
Here are all the number of line that patients received as Neoadjuvant containing platinum or taxanes.

@@

<!-- Here the lines for the 34 patient. -->
```{r, rows.print = 40}
# therapy_line %>% 
#   filter(chemotherapy_type == "Neoadjuvant" &
#            (linenumber_new == 2 | linenumber_new == 3 | linenumber_new == 4 | linenumber_new == 5)) %>% 
#   select(patientid, linename, linenumber, linenumber_new, linestartdate, lineenddate,
#          drugname, episodedate, surgerydate, chemotherapy_type) %>%
#   arrange(patientid, episodedate) %>% 
#   distinct(patientid, linenumber_new, .keep_all = TRUE) %>% 
#   select(-linenumber)

@@

`r emo::ji("question_mark")`  
Here are all the line that patients received as frontline therapy (Neo or Adj) containing platinum or taxanes should we remove more type of linename?  
Should we include patients who got a single drug as lot/line? like Carboplatin, Cisplatin, Oxaliplatin, Paclitaxel or Docetaxel by themself as a single drug?  
Should we include patients who received 1 platinum + something not taxane like Gemcitabine or others? `r emo::ji("no_entry_sign")` <span style="color:green">**Only include single or dual P/T +/- Bev in frontline treatment**</span>

```{r}
# F0017FB3A8828 starts with gemcitabine then have carbo
remove_linename_other <- therapy_line %>%
  arrange(patientid, episodedate) %>% 
  mutate(drug_count = sapply(str_split(linename, ","), length)) %>% 
  select(patientid, linename, linenumber, linenumber_new, linenumber_adj, drug_count, 
         drugname, chemotherapy_type, therapy, treatment_sequence, episodedate) %>%

  mutate(remove_linename_other = case_when(
    # keep these drugs in line 1 of upfront chemo and upfront surg
    linenumber_new == 1 & 
      drug_count == 1 &
       !str_detect(linename, "platin|taxel")                                 ~ "remove",
    linenumber_new == 1 &
      drug_count == 2 &
      (
      !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
      str_detect(linename, "platin") & str_detect(linename, "Bev") |
      str_detect(linename, "taxel") & str_detect(linename, "Bev"))
      )                                                                      ~ "remove",
    linenumber_new == 1 &
      drug_count >= 3 &
      !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))

                                                                             ~ "remove",
    # weird one
    linenumber_new == 1 &
      drug_count >= 3 &
      str_detect(linename, "Niraparib|Gemcitabine")                          ~ "remove",

    # keep these drugs in line 2 of upfront chemo from when line switch
    linenumber_new == 2 &
      therapy == "Upfront Chemo" &
      drug_count == 1 &
       !str_detect(linename, "platin|taxel")  ~ "remove",

    linenumber_new == 2 &
      therapy == "Upfront Chemo" &
      drug_count == 2 &
      (
      !(str_detect(linename, "platin") & str_detect(linename, "taxel") |
      str_detect(linename, "platin") & str_detect(linename, "Bev") |
      str_detect(linename, "taxel") & str_detect(linename, "Bev"))
      ) ~ "remove",

    linenumber_new == 2 &
      therapy == "Upfront Chemo" &
      drug_count >= 3 &
      !(str_detect(linename, "platin") & str_detect(linename, "taxel") & str_detect(linename, "Bev"))
      # !str_detect(linename, "taxel") &
      # !str_detect(linename, "Bev")
                        ~ "remove",

    TRUE                                           ~ NA_character_
  )) %>% 
  # group_by(patientid) %>% 
  # fill(remove_linename_other, .direction = "down") %>% 
  # ungroup() %>% 
  arrange(patientid, episodedate) #%>%

remove_linename_other <- remove_linename_other %>% 
  filter(remove_linename_other == "remove") %>% 
  distinct(patientid, .keep_all = T)

# remove_linename_other# <- therapy_line %>% 
  # filter(chemotherapy_type == "Neoadjuvant" &
  #          linenumber_new != 1)
remove_linename_other <- paste(remove_linename_other$patientid, collapse = "|")

therapy_line %>% 
  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
         ) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

therapy_line %>% 
  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

# therapy_line %>% distinct(patientid) %>% nrow()

therapy_line <- therapy_line %>% 
  # Remove patients with other linename
  filter(!str_detect(patientid, remove_linename_other)) %>% 
  arrange(patientid, episodedate)
# example of keep
```

```{r}
therapy_line %>% 
  filter(linenumber == 1#, treatment_sequence == "neo + surg + adj"
         ) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

therapy_line %>% 
  filter(linenumber_new == 2, therapy == "Upfront Chemo") %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linename) %>% 
  tbl_summary(sort = list(everything() ~ "frequency"))

@@

Number of Neoadjuvant line in patients with upfront neo (only 1 line because we excluded patients with more)
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront neo
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of Adjuvant line in patients with upfront surgery
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
<br>

@@

@@

```{r RDI calculation}
Frontline <- Treatment %>% 
  # Calculate 1 RDI per drug per day, for whole Neoadjuvant and for first line of Adjuvant
  #   group_by(patientid, chemotherapy_type) %>% 
  # mutate(linenumber_adj = dense_rank(linenumber_new)) %>%

@@

  # Average RDI by taxel or platin by line (will NOT combine pacli-doce and cis-carbo-oxalo)
  group_by(patientid, chemotherapy_type, drugname_type) %>%
  mutate(mean_RDI_per_chemotype_drug = case_when(
    chemotherapy_type == "Adjuvant" &
      linenumber_adj == 1                  ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3),
    chemotherapy_type == "Neoadjuvant"     ~ round(mean(relative_dose_intensity, na.rm = TRUE), 3)
  )) %>% 
  ungroup() %>% 
  distinct(patientid, chemotherapy_type, drugname_type, .keep_all = TRUE) %>% 
  mutate(RDI_grp = case_when(
    mean_RDI_per_chemotype_drug >= 0.85              ~ "correct",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("correct", "underdose"))) %>% 
  mutate(RDI_grp1 = case_when(
    mean_RDI_per_chemotype_drug < 0.75               ~ "highly underdose",
    mean_RDI_per_chemotype_drug < 0.85               ~ "underdose",
    mean_RDI_per_chemotype_drug < 1                  ~ "correct",
    mean_RDI_per_chemotype_drug == 1                 ~ "perfect",
    mean_RDI_per_chemotype_drug < 1.5                ~ "higher dose",
    mean_RDI_per_chemotype_drug >= 1.5               ~ "overdose"
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("highly underdose", "underdose", "correct", "perfect", "higher dose", "overdose")))
```

@@

## 2.Plots Clinical
<div class = "row">
<div class = "col-md-6">
```{r plot clinical}
Frontline %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

@@

<span style="color:green">**Table . Summary treatment data by race**</span>

```{r treatment table}
# tbl1 <- 
  Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  select(c(raceeth, #delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
           "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
           had_neo, had_adj,
           "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
           )) %>% 
  tbl_summary(by = raceeth) %>% bold_labels() %>% add_overall() %>% add_p(
    # test.args = all_tests("chisq.test") ~ list(workspace=2e9)
    ) %>% bold_p(t = .05)
# tbl2 <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
#   filter(exclude != "1") %>% 
#   select(c(raceeth, delay_incare_dx_to_treat, #mean_skipped_cycle_indays,
#            "issurgery", "extentofdebulking", "resdz", "debulking", "diff_surg_dx",
#            "chemotherapy_type", "therapy", "treatment_sequence"#, "relative_dose_intensity", "RDI_grp"
#            )) %>% 
#   tbl_summary(by = raceeth, missing = "no") %>% bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
# tbl_merge(list(tbl1, tbl2), tab_spanner = c("with unknown", "without unknown"))
```
<br>

## 2.Plots Treatment
<div class = "row">
<div class = "col-md-6">
```{r treatment plots}
Frontline %>%
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= therapy))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Frontline treatment")+
  coord_flip()

@@

<div class = "row">
<div class = "col-md-6">
```{r treatment survival, fig.height = 7}
# OS by extentofdebulking
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ extentofdebulking, data=Frontline %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

@@

```{r Table 4}
# Treatment & demo
tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl3 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/adjuvant \nUpfront Chemo \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl4 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "carboplatin" & chemotherapy_type == "Neoadjuvant") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "carb/neoadjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl5 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(drugname == "cisplatin" & chemotherapy_type == "Adjuvant" & therapy == "Upfront Surgery") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat,  "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "cis/adjuvant \nUpfront Surgery \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl6 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))

tbl1 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(raceeth, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = raceeth,
              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl2 <- Frontline %>% filter(str_detect(drugname, "cisplatin") & chemotherapy_type == "Adjuvant" & therapy == "Upfront Chemo") %>%
  filter(exclude != "1") %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(c(bmi_cat, "relative_dose_intensity", RDI_grp)) %>%
  tbl_summary(by = bmi_cat,
              label = list(relative_dose_intensity ~ "cisplatin/adjuvant \nRDI")) %>%
  bold_labels() %>% add_overall() %>% add_p() %>% bold_p(t = .05)
tbl7 <-
  tbl_merge(list(tbl1, tbl2), tab_spanner = c("Race/Ethnicity", "BMI"))
